Enhanced Residual Context-based Networks for Image Outpainting

### 2020-05-10 tex/paper.tex
Added tables to report

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Title of My Paper}

@@

\twocolumn[
\icmltitle{Title of My Paper}

@@

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{wpi}
\icmlauthor{Bauiu C.~Yyyy}{wpi}
\end{icmlauthorlist}

@@

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@wpi.edu}

@@

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Enhanced Residual Context-based Networks for Image Outpainting}

@@

\twocolumn[
\icmltitle{Enhanced Residual Context-based Networks for Image Outpainting}

@@

\begin{icmlauthorlist}
\icmlauthor{Przemek Gardias}{wpi}
\icmlauthor{Eric Arthur}{wpi}
\icmlauthor{Huaming Sun}{wpi}
\end{icmlauthorlist}

@@

\icmlcorrespondingauthor{Przemek Gardias}{pmgardias@wpi.edu}

@@

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c|c}  
    \hline
    \textbf{layer} & \textbf{output size} & \textbf{parameters}\\ 
    \hline
      Conv & 16$\times$192$\times$192 & 5$\times$5, stride=1 \\
    \hline
      ResBlock & 128$\times$96$\times$96 & 3$\times$3, stride=2 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=2 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Trans-Conv & 128$\times$96$\times$96 & 4$\times$4, stride=1 \\
    \hline
      ReLU & 128$\times$96$\times$96 & None \\
    \hline
      Conv & 128$\times$96$\times$96 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 128$\times$96$\times$96 & None \\
    \hline
      Trans-Conv & 64$\times$192$\times$192 & None \\
    \hline
      ReLU & 64$\times$192$\times$192 & None \\
    \hline
      Conv & 32$\times$192$\times$192 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 32$\times$192$\times$192 & None \\
    \hline
      Conv & 3$\times$192$\times$192 & 3$\times$3, stride=2 \\
    \hline
      Sigmoid & 3$\times$192$\times$192 & None \\
    \hline
    \end{tabular}

  \caption{Architecture of generator, including parameters. Trans-Conv is transposed convolution.} 
  \label{tab:1}
  \label{table1} 
\end{table}

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c}  
    \hline
    \textbf{layer} & \textbf{parameters}\\ 
    \hline
      Conv & 3$\times$3, stride=\(s_{in}\) \\
    \hline
      ReLU & None \\
    \hline
      Conv & 3$\times$3, stride=\(s_{in}\) \\
    \hline
      ReLU & None \\
    \hline
      Add & None \\
    \hline
    \end{tabular}

  \caption{Architecture of residual block used in generator, including parameters. The residual block applies input strides \(s_{in}\) as convolution layer parameters. Add is an element-wise addition of \(x_{in}\) and output tensor of previous layer.} 
  \label{tab:2}
  \label{table2} 
\end{table}

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c}  
    \hline
    \textbf{layer} & \textbf{parameters}\\ 
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=1 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=1 \\
    \hline

    \end{tabular}

  \caption{Architecture of global and local discriminators.} 
  \label{tab:3}
  \label{table3} 
\end{table}
